Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-10-09 analysis/paper/supplement.Rmd
Ongoing - manuscript and method tweaking.
Draft MS sent to co-authors

|$N_t$|animals|Adult female population size.|
|$\bar{\lambda}_{y,t}$|rate|Average population growth over $y$ years.|
|$X_t$|rate|Recruitment adjusted for sex ratio and misidentification bias.|
|$W_t$|animals|Surviving adult females before recruitment.|
|$J_t$|animals|New recruits to adult age class.|
|$\lambda_t$|rate|Annual population growth.|

@@

@@

@@

@@

|$k=50000$||Carrying capacity.|

@@

|$y=3$|years|Assessment period for population growth rate.|

>>>>

|$X_t$|rate|Recruitment adjusted for sex ratio and composition survey errors.|

@@

|$\tilde{lambda}_{t}$|rate|Expected annual population growth.|

@@

|$\dot{\lambda}_t$|rate|Annual population growth.|
|$\bar{lambda}_{t}$|rate|Expected annual population growth.|

@@

|$\phi^R \sim \text{Normal}(19.862,2.229)$||Precision of recruitment-disturbance relationship.|
|$\phi^S \sim \text{Normal}(63.733,8.311)$||Precision of survival-disturbance relationship.|

@@

|$k=10000$||Carrying capacity.|

@@
